### 2019-04-02 Abstract.tex
Updates from Overleaf

Our formulation is derived from a principled notion of set probability, as the sum of probabilities of corresponding permutation \blue{permutation} sequences for the set. We provide a new training objective that maximizes this set probability, and a new prediction objective that finds the most probable set on test documents. These new objectives are theoretically appealing because they give the RNN model freedom to discover the best label order, which often is the natural one (but different among documents).

>>>>

Our formulation is derived from a principled notion of set probability, as the sum of probabilities of corresponding permutation sequences for the set. We provide a new training objective that maximizes this set probability, and a new prediction objective that finds the most probable set on test documents. These new objectives are theoretically appealing because they give the RNN model freedom to discover the best label order, which often is the natural one (but different among documents).

### 2019-04-02 Introduction.tex
Updates from Overleaf

Recurrent neural networks (RNN) are originally designed to output a sequential structure, such as a sentence \cite{DBLP:conf/emnlp/ChoMGBBSB14}.  Recently, RNNs have also been applied to multi-label classification by mapping the label set to a sequence \cite{DBLP:conf/cvpr/WangYMHHX16,DBLP:journals/corr/ZhangWSZL16,DBLP:conf/icpr/JinN16,DBLP:conf/iccv/WangCLXL17,DBLP:journals/corr/abs-1709-08553,DBLP:conf/aaai/ChenCYW18,DBLP:journals/corr/abs-1806-04822}. In contrast to PCC where a binary decision is made for each label sequentially,  RNN only predicts the positive labels explicitly and therefore its decision chain length is equal to the number of positive labels, not the number of all labels.  Therefore RNN, while still suffers from early errors, propagates errors less than PCC.

@@

Both PCC and RNN rely heavily on label orders in training and prediction. In multi-label data, the labels are given as sets, not necessarily with natural order.  RNN define a sequence probability (dynamically) while PCC define set probability (statically, sets are built in a predefined order). Various ways of arranging sets as sequences have been explored:  ordered alphabetically,  by frequency, based on a label hierarchy, or according to some label ranking algorithm \cite{liu2015optimality}. The experimental results show that which order to choose can have a significant impact on learning and prediction \cite{vinyals2015order,DBLP:conf/nips/NamMKF17,DBLP:conf/aaai/ChenCYW18}. In the above example, starting label predictions sequence with \texttt{Russia}, while correct, would make the other predictions very difficult.

Previous work has shown that it is possible to train an RNN on multi-label data without specifying the label order in advance. With special training objectives, RNNs can explore different label orders and converge to some order automatically \cite{vinyals2015order}. In this paper we follow the same line of study: We consider how to adapt RNN sequence model to multi-label set prediction without specifying the label order. Specifically, we make the following  contributions:
\begin{enumerate}
\item We analyze existing RNNs models proposed for multi-label prediction, and show that existing training and prediction objectives are not well justified mathematically and have undesired consequences in practice. 
% \item We are the first to make a clear distinction between sequence probability and set probability (in this learning setup), and treat set probability naturally as the sum of all corresponding sequence probabilities.
% \item Based on this set probability definition, we derive new training and prediction objectives that avoid the drawbacks of existing ones, and give the RNN model more freedom to automatically discover and utilize the best label orders.
\item  We develop efficient approximate training and prediction methods. We propose new training and prediction objectives based on a principled notion of set probability. Our new formulation avoids the drawbacks of existing ones and gives  the  RNN  model  freedom  to discover the best label order. 
\item We outperform state-of-the-art methods on several multi-label classification datasets.
\end{enumerate}
 % In this paper, we instead train RNNs by directly maximizing the probability of the \emph{label set}, which is defined as the sum of all sequence (set-permutations) probabilities---thus not constrained by a particular order.
 % % This approach gives the model the freedom to explore different orders in training and prediction and leads to better prediction performance. 
 % Our results on benchmark data sets demonstrate that our proposed method outperforms state-of-the-art methods for the task of multi-label set prediction.

\section{Mapping Sequences to Sets} 
In this section, we formulate how existing works map sequences to sets, by writing down their objective functions using consistent notations. To review RNN designed for sequences, let $\mathbf{s}=(s_1,s_2,...,s_T)$ be an input sequence of outcomes, in a particular order, where $T$ is the maximum number of labels in a document; the order is often critical to the datapoint. An RNN model defines a probability distribution over all possible output sequences given the input in the form $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)=\prod_{t=1}^T p(s_t|x,s_1,s_2,...,s_{t-1})$. To train the RNN model, one maximizes the likelihood of the ground truth sequence $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)$.

At prediction time, one seeks to find the sequence with the highest probability $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$, and this is usually implemented approximately with a beam search procedure \cite{lowerre1976harpy} (we modified into Algorithm \ref{alg:beam_combine}). The sequence history is encoded with an internal memory vector $h_t$ which is updated over time. RNN is also often equipped with the attention mechanism \cite{DBLP:journals/corr/BahdanauCB14}, which in each timestep $t$ puts different weights on different words (features) and thus effectively attends on a list of important words. The context vector of selected words $c_t$ is computed as the weighted average over the dense representation of the words. The context $c_t$, the RNN memory $h_t$ at timestep $t$, and the previous label ${s_{t-1}}$ are concatenated and used to model the label probability distribution at time $t$ as $p(s_t|x,s_1,s_2,...,s_{t-1}) \sim  \softmax(\phi(c_t,h_t,s_{t-1}))$, where $\phi$ is a non-linear function, and $\softmax$ is the normalized exponential function generalizing binary logistic regression. %Other variants of RNN, such as sequence to sequence encoder-decoder structure \cite{DBLP:conf/emnlp/ChoMGBBSB14,DBLP:conf/nips/NamMKF17}, further take into account the word order in the documents. \kechen{remove last sentence?}

@@

 To apply RNNs to multi-label problems, one has to map the given set of labels $\mathbf{y}$ to a sequence $\mathbf{s}=(s_1,s_2,...,s_T)$, on training documents. This is usually obtained by writing the label set in a globally fixed order (e.g.\ by label frequency), similar to PCC.
 % After mapping the ground truth set $\mathbf{y}^{(n)}$ to a sequence $\mathbf{s}^{(n)}$ with the chosen order for each training instance $(x^{(n)},\mathbf{y}^{(n)})$,
 Once mapping is done, RNN are trained with the standard maximum likelihood objective \cite{DBLP:conf/nips/NamMKF17}: 
\begin{align}
\maximize \sum_{n=1}^N \log p(\mathbf{s}^{(n)}|x^{(n)})
\label{eq:standard_rnn}
\end{align}
where $N$ is the total number of documents in the corpus. \newcite{vinyals2015order} proposes to dynamically choose during training the sequence order deemed as most probable by the current RNN model:
\begin{align}
\maximize \sum_{n=1}^N \max_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})}\log p(\mathbf{s}|x^{(n)})
\label{eq:max_obj}
%\vspace{-2ex}
\end{align}
where the $\pi(\mathbf{y}^{(n)})$ stands for all  permutations of $\mathbf{y}^{(n)}$. This eliminates the need to manually specify label order.
However, as noticed by the authors, this objective cannot be used in the early training stages: the early order choice (often random) is reinforced by this objective and can be stuck upon permanently. To address this issue, \newcite{vinyals2015order}~also proposes two smoother alternative objectives to initialize the model training:

>>>>

Recurrent neural network (RNN) is originally designed to output a sequential structure, such as a sentence \cite{DBLP:conf/emnlp/ChoMGBBSB14}.  Recently, RNNs have also been applied to multi-label classification by mapping the label set to a sequence \cite{DBLP:conf/cvpr/WangYMHHX16,DBLP:journals/corr/ZhangWSZL16,DBLP:conf/icpr/JinN16,DBLP:conf/iccv/WangCLXL17,DBLP:journals/corr/abs-1709-08553,DBLP:conf/aaai/ChenCYW18,DBLP:journals/corr/abs-1806-04822}. In contrast to PCC where a binary decision is made for each label sequentially,  RNN only predicts the positive labels explicitly and therefore its decision chain length is equal to the number of positive labels, not the number of all labels.  Therefore RNN, while still suffers from early errors, propagates errors less than PCC.

@@

Both PCC and RNN rely heavily on label orders in training and prediction. In multi-label data, the labels are given as sets, not necessarily with natural order.  RNN defines a sequence probability (dynamically) while PCC defines set probability (statically, sets are built in a predefined order). Various ways of arranging sets as sequences have been explored:  ordered alphabetically,  by frequency, based on a label hierarchy, or according to some label ranking algorithm \cite{liu2015optimality}. The experimental results show that which order to choose can have a significant impact on learning and prediction \cite{vinyals2015order,DBLP:conf/nips/NamMKF17,DBLP:conf/aaai/ChenCYW18}. In the above example, starting label predictions sequence with \texttt{Russia}, while correct, would make the other predictions very difficult.

Previous work has shown that it is possible to train an RNN on multi-label data without specifying the label order in advance. With special training objectives, RNN can explore different label orders and converge to some order automatically \cite{vinyals2015order}. In this paper we follow the same line of study: We consider how to adapt RNN sequence model to multi-label set prediction without specifying the label order. Specifically, we make the following  contributions:
\begin{enumerate}
\item We analyze existing RNN models proposed for multi-label prediction, and show that existing training and prediction objectives are not well justified mathematically and have undesired consequences in practice. 
% \item We are the first to make a clear distinction between sequence probability and set probability (in this learning setup), and treat set probability naturally as the sum of all corresponding sequence probabilities.
% \item Based on this set probability definition, we derive new training and prediction objectives that avoid the drawbacks of existing ones, and give the RNN model more freedom to automatically discover and utilize the best label orders.
\item  We develop efficient approximate training and prediction methods. We propose new training and prediction objectives based on a principled notion of set probability. Our new formulation avoids the drawbacks of existing ones and gives  the  RNN  model  freedom  to discover the best label order. 
\item We outperform state-of-the-art methods on several multi-label classification datasets.
\end{enumerate}
 % In this paper, we instead train RNNs by directly maximizing the probability of the \emph{label set}, which is defined as the sum of all sequence (set-permutations) probabilities---thus not constrained by a particular order.
 % % This approach gives the model the freedom to explore different orders in training and prediction and leads to better prediction performance. 
 % Our results on benchmark data sets demonstrate that our proposed method outperforms state-of-the-art methods for the task of multi-label set prediction.

\section{Mapping Sequences to Sets} 
In this section, we formulate how existing approaches map sequences to sets, by writing down their objective functions using consistent notations. To review RNN designed for sequences, let $\mathbf{s}=(s_1,s_2,...,s_T)$ be an input sequence of outcomes, in a particular order, where $T$ is the maximum number of labels in a document; the order is often critical to the datapoint. An RNN model defines a probability distribution over all possible output sequences given the input in the form $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)=\prod_{t=1}^T p(s_t|x,s_1,s_2,...,s_{t-1})$. To train the RNN model, one maximizes the likelihood of the ground truth sequence $p(\mathbf{s}=(s_1,s_2,...,s_T)|x)$.

At prediction time, one seeks to find the sequence with the highest probability $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$, and this is usually implemented approximately with a beam search procedure \cite{lowerre1976harpy} (we modified into Algorithm \ref{alg:beam_combine}). The sequence history is encoded with an internal memory vector $h_t$ which is updated over time. RNN is also often equipped with the attention mechanism \cite{DBLP:journals/corr/BahdanauCB14}, which in each timestep $t$ puts different weights on different words (features) and thus effectively attends on a list of important words. The context vector $c_t$ is computed as the weighted average over the dense representation of these words to capture information from the document. The context $c_t$, the RNN memory $h_t$ at timestep $t$, and the previous label ${s_{t-1}}$ are concatenated and used to model the label probability distribution at time $t$ as $p(s_t|x,s_1,s_2,...,s_{t-1}) \sim  \softmax(\phi(c_t,h_t,s_{t-1}))$, where $\phi$ is a non-linear function, and $\softmax$ is the normalized exponential function generalizing binary logistic regression. %Other variants of RNN, such as sequence to sequence encoder-decoder structure \cite{DBLP:conf/emnlp/ChoMGBBSB14,DBLP:conf/nips/NamMKF17}, further take into account the word order in the documents. \kechen{remove last sentence?}

@@

 To apply RNNs to multi-label problems, one has to map the given set of labels $\mathbf{y}$ to a sequence $\mathbf{s}=(s_1,s_2,...,s_T)$, on training documents. This is usually obtained by writing the label set in a globally fixed order (e.g.\ by label frequency), similar to PCC.
 % After mapping the ground truth set $\mathbf{y}^{(n)}$ to a sequence $\mathbf{s}^{(n)}$ with the chosen order for each training instance $(x^{(n)},\mathbf{y}^{(n)})$,
 Once mapping is done, RNN are trained with the standard maximum likelihood objective \cite{DBLP:conf/nips/NamMKF17}: 
\begin{align}
\maximize \sum_{n=1}^N \log p(\mathbf{s}^{(n)}|x^{(n)})
\label{eq:standard_rnn}
\end{align}
where $N$ is the total number of documents in the corpus. \newcite{vinyals2015order} proposes to dynamically choose during training the sequence order deemed as most probable by the current RNN model:
\begin{align}
\maximize \sum_{n=1}^N \max_{\mathbf{s}\in \pi(\mathbf{y}^{(n)})}\log p(\mathbf{s}|x^{(n)})
\label{eq:max_obj}
%\vspace{-2ex}
\end{align}
where the $\pi(\mathbf{y}^{(n)})$ stands for all  permutations of $\mathbf{y}^{(n)}$. This eliminates the need to manually specify the label order.
However, as noticed by the authors, this objective cannot be used in the early training stages: the early order choice (often random) is reinforced by this objective and can be stuck upon permanently. To address this issue, \newcite{vinyals2015order}~also proposes two smoother alternative objectives to initialize the model training:

### 2019-04-02 Model.tex
Updates from Overleaf

We propose a new way of adapting RNN to multi-label set prediction, which we call \emph{set-RNN}. We appreciate the RNN model structure (defines a probability distribution over all possible sequences directly) and introduce training and prediction objectives tailored for sets that take advantage of it, while making a clear distinction between the sequence probability $p(\mathbf{s}|x)$ and the set probability $p(\mathbf{y}|x)$. 
% We notice that previous work either lack an explicit definition of set probability, or use sequence probability as the set probability, or transform sequence probability into set probability in an ad hoc way. 
% We notice that while the idea of using RNN for multi-label prediction has a lot of advantages and potentials, the existing adaptations of RNN to set prediction task are not well justified and have several issues.
 % In the literature, these two are often used interchangeably.
 % A standard RNN model only defines a probability distribution over all possible sequences directly, as mentioned earlier.
  We define the set probability as the sum of sequences probabilities for all sequence permutations of the set, namely $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. Based on this formulation, an RNN also defines a probability distribution over all possible sets indirectly since $\sum_{\mathbf{y}} p(\mathbf{y}|x)=\sum_{\mathbf{y}}\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)=\sum_{\mathbf{s}} p(\mathbf{s}|x)=1$.   
  % \kechen{It's still possible for the model to predict a label twice. I'd like to see a mathematical treatment of this case in your framework. Would you treat the predicted multiset as a set by ignoring repeated entries? Would you force the probability of a multiset down to zero? The mere fact that these can be predicted by the model means that they should eat away at some of the probability mass devoted to pure sets. You need a way of handling this. }
  To be precise, our label ``permutations'' $\pi$ are sequences that allow repetitions (i.e. $(y_1,y_2,y_3,y_1,...)$), up to a maximum length. So the set probability sums over all such permutations, and both training and prediction candidate sets are generated this way. In practice, we dont think this detail makes any difference, as sequences with repeated labels are extremely rare; however in theory we want to allow the attention context to focus on any recent labels it chooses to (repeated if necessary).

@@

If only some sequence permutations receive high probabilities while others receive low probabilities, the set probability will still be low. In other words, if for each document, RNN finds one  good way of ordering relevant labels (such as hierarchically) and allocates most of the probability mass to the sequence in that order, the model will be penalized heavily.  As a consequence the model has little freedom in discovering and concentrating on some natural label order. In contrast, with our proposed training objective, in which the multiplication operation is replaced by the  summation operation, it suffices to find only one reasonable permutation of the labels for each document. \emph{Different documents can have different label orders}; thus our proposed training objective gives the RNN model far more freedom on label order. The other two objectives (\ref{eq:max_obj}) and (\ref{eq:sample_obj}) proposed in \cite{vinyals2015order} are less restrictive than  (\ref{eq:wrong_obj}), but they have to work in conjunction with (\ref{eq:wrong_obj}) because of the self reinforcement issue. Our proposed training objective has a natural probabilistic interpretation, does not suffer from self reinforcement issue and can serve as a stand alone training objective. 
% Another approach used in previous work, which is to pick one fixed sequence order (e.g., by label frequency) in advance, forces the model to only assign high probabilities to sequences in that order.
% , and therefore does not leave any opportunity for the model to explore label orders. Since in multi-label data, labels often do not have an obvious ordering and human heuristics are often suboptimal, it is advantageous to let the training procedure discover label orderings, on a per sample basis.
% \subsection{A Brief Review of RNN and Attention}

>>>>

We propose a new way of adapting RNN to multi-label set prediction, which we call \emph{set-RNN}. We appreciate the RNN model structure \cite{rumelhart1988learning} (defines a probability distribution over all possible sequences directly) and introduce training and prediction objectives tailored for sets that take advantage of it, while making a clear distinction between the sequence probability $p(\mathbf{s}|x)$ and the set probability $p(\mathbf{y}|x)$. 
% We notice that previous work either lack an explicit definition of set probability, or use sequence probability as the set probability, or transform sequence probability into set probability in an ad hoc way. 
% We notice that while the idea of using RNN for multi-label prediction has a lot of advantages and potentials, the existing adaptations of RNN to set prediction task are not well justified and have several issues.
 % In the literature, these two are often used interchangeably.
 % A standard RNN model only defines a probability distribution over all possible sequences directly, as mentioned earlier.
  We define the set probability as the sum of sequences probabilities for all sequence permutations of the set, namely $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. Based on this formulation, an RNN also defines a probability distribution over all possible sets indirectly since $\sum_{\mathbf{y}} p(\mathbf{y}|x)=\sum_{\mathbf{y}}\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)=\sum_{\mathbf{s}} p(\mathbf{s}|x)=1$.   
  % \kechen{It's still possible for the model to predict a label twice. I'd like to see a mathematical treatment of this case in your framework. Would you treat the predicted multiset as a set by ignoring repeated entries? Would you force the probability of a multiset down to zero? The mere fact that these can be predicted by the model means that they should eat away at some of the probability mass devoted to pure sets. You need a way of handling this. }
  To be precise, our label ``permutations'' $\pi$ are sequences that allow repetitions (i.e.\ $(y_1,y_2,y_3,y_1,...)$), up to a maximum length. So the set probability sums over all such permutations, and both training and prediction candidate sets are generated this way. In practice, we do not think this detail makes any difference, as sequences with repeated labels are extremely rare; however in theory we want to allow the attention context to focus on any recent labels it chooses to (repeated if necessary).

@@

If only some sequence permutations receive high probabilities while others receive low probabilities, the set probability will still be low in Eq. 3. In other words, if for each document, RNN finds one  good way of ordering relevant labels (such as hierarchically) and allocates most of the probability mass to the sequence in that order, the model will be penalized heavily.  As a consequence the model has little freedom in discovering and concentrating on some natural label order. In contrast, with our proposed training objective, in which the multiplication operation is replaced by the  summation operation, it suffices to find only one reasonable permutation of the labels for each document. \emph{Different documents can have different label orders}; thus our proposed training objective gives the RNN model far more freedom on label order. The other two objectives (\ref{eq:max_obj}) and (\ref{eq:sample_obj}) proposed in \cite{vinyals2015order} are less restrictive than  (\ref{eq:wrong_obj}), but they have to work in conjunction with (\ref{eq:wrong_obj}) because of the self reinforcement issue. Our proposed training objective has a natural probabilistic interpretation, does not suffer from self reinforcement issue and can serve as a stand alone training objective. 
% Another approach used in previous work, which is to pick one fixed sequence order (e.g., by label frequency) in advance, forces the model to only assign high probabilities to sequences in that order.
% , and therefore does not leave any opportunity for the model to explore label orders. Since in multi-label data, labels often do not have an obvious ordering and human heuristics are often suboptimal, it is advantageous to let the training procedure discover label orderings, on a per sample basis.
% \subsection{A Brief Review of RNN and Attention}
